RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2023-02-02 jsac.tex
:lipstick: Update illustrations

\begin{section}{RIScatter}
	% \begin{subsection}{Concepts}
	We propose RIScatter in Fig.~\subref*{fg:riscatter} as a generalization of \gls{bc} and \gls{ris}, which involves coexisting active primary and passive backscatter links in a flexible and mutualistic manner.
	RIScatter nodes leverage \gls{csi}- and \gls{qos}-based reflection state distribution design to smoothly transition between backscatter modulation and passive beamforming.
	Fig.~\ref{fg:riscatter_node} illustrates the block diagram, equivalent circuit, and scatter model of a RIScatter node.
	It can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
	\begin{figure*}[!t]
		\centering
		\subfloat[Block Diagram]{
			\resizebox{0.32\linewidth}{!}{
				\input{assets/illustration/block_diagram.tex}
			}
			\label{fg:block_diagram}
		}
		\subfloat[Equivalent Circuit]{
			\resizebox{0.37\linewidth}{!}{
				\input{assets/illustration/equivalent_circuit.tex}
			}
			\label{fg:equivalent_circuit}
		}
		\subfloat[Scatter Model]{
			\resizebox{0.28\linewidth}{!}{
				\input{assets/illustration/scatter_model.tex}
			}
			\label{fg:scatter_model}
		}
		\caption{
		Block diagram, equivalent circuit, and scatter model of a RIScatter node.
		The solid and dashed vectors represent signal and energy flows.
		The scatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\text{I}}$ and magnetic field $\vec{H}_{\text{I}}$ \cite{Huang2021}.
		}
		\label{fg:riscatter_node}
	\end{figure*}
	Fig.~\ref{fg:scatter_comparison} compares the reflection state distribution and reflection pattern of RIScatter and other applications.
	\begin{figure}[!t]
		\centering
		\subfloat[Reflection State Distribution]{
			\resizebox{0.32\columnwidth}{!}{
				\input{assets/illustration/input_distribution.tex}
			}
			\label{fg:input_distribution}
		}
		\subfloat[Reflection Pattern]{
			\resizebox{0.32\columnwidth}{!}{
				\input{assets/illustration/time_structure.tex}
			}
			\label{fg:time_structure}
		}
		\caption{
			Reflection state distribution and reflection pattern over time of scattering applications.
			``PB'', ``BB'', and ``CB'' means primary block, backscatter block, and channel block, respectively.
			\gls{bc} employs all possible states only as information codewords, \gls{ris} treats them only as beamformer codewords, and RIScatter simultaneously exploits both benefits.
		}
		\label{fg:scatter_comparison}
	\end{figure}
	Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node \emph{semi-randomly} chooses the reflection state for each backscatter block with \emph{guidance of input probability} $P(\Gamma_m)$ at state $m$.
	Such an adaptive backscatter channel coding includes the degenerate distribution of \gls{ris} and the uniform distribution of line-coded \gls{bc} as special cases.
	Importantly, RIScatter system design only requires the \emph{direct} transmitter-receiver and \emph{cascaded} transmitter-scatter-receiver \gls{csi}.
	For dispersed RIScatter nodes, relevant \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
	For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.

>>>>

\begin{section}{RIScatter}
	% \begin{subsection}{Concepts}
	We propose RIScatter in Fig.~\subref*{fg:riscatter} as a generalization of \gls{bc} and \gls{ris}, which involves coexisting active primary and passive backscatter links in a flexible and mutualistic manner.
	RIScatter nodes leverage \gls{csi}- and \gls{qos}-based reflection state distribution design to smoothly transition between backscatter modulation and passive beamforming.
	Fig.~\ref{fg:riscatter_node} illustrates the block diagram, equivalent circuit, and scatter model of a RIScatter node.
	It can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
	\begin{figure*}[!t]
		\centering
		\subfloat[Block Diagram]{
			\resizebox{0.32\linewidth}{!}{
				\input{assets/illustration/block_diagram.tex}
			}
			\label{fg:block_diagram}
		}
		\subfloat[Equivalent Circuit]{
			\resizebox{0.37\linewidth}{!}{
				\input{assets/illustration/equivalent_circuit.tex}
			}
			\label{fg:equivalent_circuit}
		}
		\subfloat[Scatter Model]{
			\resizebox{0.28\linewidth}{!}{
				\input{assets/illustration/scatter_model.tex}
			}
			\label{fg:scatter_model}
		}
		\caption{
		Block diagram, equivalent circuit, and scatter model of a RIScatter node.
		The solid and dashed vectors represent signal and energy flows.
		The scatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\text{I}}$ and magnetic field $\vec{H}_{\text{I}}$ \cite{Huang2021}.
		}
		\label{fg:riscatter_node}
	\end{figure*}
	Fig.~\ref{fg:scatter_comparison} compares the reflection state distribution and reflection pattern of RIScatter and other applications.
	\begin{figure}[!t]
		\centering
		\subfloat[Reflection State Distribution]{
			\resizebox{0.32\columnwidth}{!}{
				\input{assets/illustration/input_distribution.tex}
			}
			\label{fg:input_distribution}
		}
		\subfloat[Reflection Pattern]{
			\resizebox{0.32\columnwidth}{!}{
				\input{assets/illustration/time_structure.tex}
			}
			\label{fg:time_structure}
		}
		\caption{
			Reflection state distribution and reflection pattern over time of scattering applications.
			``PB'', ``BB'', and ``CB'' refer to primary block, backscatter block, and channel block, respectively.
			\gls{bc} employs all possible states as information codewords, \gls{ris} treats them as beamformer codewords, and RIScatter simultaneously exploits both benefits.
		}
		\label{fg:scatter_comparison}
	\end{figure}
	Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node \emph{semi-randomly} chooses the reflection state for each backscatter block with \emph{guidance of input probability} $P(\Gamma_m)$ at state $m$.
	Such an adaptive backscatter channel coding includes the degenerate distribution of \gls{ris} and the uniform distribution of line-coded \gls{bc} as special cases.
	Importantly, RIScatter system design only requires the \emph{direct} transmitter-receiver and \emph{cascaded} transmitter-scatter-receiver \gls{csi}.
	For dispersed RIScatter nodes, relevant \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
	For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.

### 2023-02-02 main.tex
:lipstick: Update illustrations

\begin{section}{RIScatter}
	\begin{subsection}{Concepts}
		We propose RIScatter in Fig.~\subref*{fg:riscatter} as a generalization of \gls{bc} and \gls{ris}, which involves coexisting active primary and passive backscatter links in a flexible and mutualistic manner.
		RIScatter nodes leverage \gls{csi}- and \gls{qos}-based reflection state distribution design to smoothly transition between backscatter modulation and passive beamforming.
		Fig.~\ref{fg:riscatter_node} illustrates the block diagram, equivalent circuit, and scatter model of a RIScatter node.
		It can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
		\begin{figure*}[!t]
			\centering
			\subfloat[Block Diagram]{
				\resizebox{0.32\linewidth}{!}{
					\input{assets/illustration/block_diagram.tex}
				}
				\label{fg:block_diagram}
			}
			\subfloat[Equivalent Circuit]{
				\resizebox{0.37\linewidth}{!}{
					\input{assets/illustration/equivalent_circuit.tex}
				}
				\label{fg:equivalent_circuit}
			}
			\subfloat[Scatter Model]{
				\resizebox{0.28\linewidth}{!}{
					\input{assets/illustration/scatter_model.tex}
				}
				\label{fg:scatter_model}
			}
			\caption{
			Block diagram, equivalent circuit, and scatter model of a RIScatter node.
			The solid and dashed vectors represent signal and energy flows.
			The scatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\text{I}}$ and magnetic field $\vec{H}_{\text{I}}$ \cite{Huang2021}.
			}
			\label{fg:riscatter_node}
		\end{figure*}
		Fig.~\ref{fg:scatter_comparison} compares the reflection state distribution and reflection pattern of RIScatter and other applications.
		\begin{figure}[!t]
			\centering
			\subfloat[Reflection State Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
				\label{fg:input_distribution}
			}
			\\
			\subfloat[Reflection Pattern]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_structure.tex}
				}
				\label{fg:time_structure}
			}
			\caption{
				Reflection state distribution and reflection pattern over time of scattering applications.
				``PB'', ``BB'', and ``CB'' means primary block, backscatter block, and channel block, respectively.
				\gls{bc} employs all possible states only as information codewords, \gls{ris} treats them only as beamformer codewords, and RIScatter simultaneously exploits both benefits.
			}
			\label{fg:scatter_comparison}
		\end{figure}
		Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node \emph{semi-randomly} chooses the reflection state for each backscatter block with \emph{guidance of input probability} $P(\Gamma_m)$ at state $m$.
		Such an adaptive backscatter channel coding includes the degenerate distribution of \gls{ris} and the uniform distribution of line-coded \gls{bc} as special cases.
		Importantly, RIScatter system design only requires the \emph{direct} transmitter-receiver and \emph{cascaded} transmitter-scatter-receiver \gls{csi}.
		For dispersed RIScatter nodes, relevant \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
		For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.

>>>>

\begin{section}{RIScatter}
	\begin{subsection}{Concepts}
		We propose RIScatter in Fig.~\subref*{fg:riscatter} as a generalization of \gls{bc} and \gls{ris}, which involves coexisting active primary and passive backscatter links in a flexible and mutualistic manner.
		RIScatter nodes leverage \gls{csi}- and \gls{qos}-based reflection state distribution design to smoothly transition between backscatter modulation and passive beamforming.
		Fig.~\ref{fg:riscatter_node} illustrates the block diagram, equivalent circuit, and scatter model of a RIScatter node.
		It can be implemented by adding an integrated receiver \cite{Kim2021a} and adaptive encoder \cite{He2020e} to off-the-shelf passive \gls{rfid} tags.
		\begin{figure*}[!t]
			\centering
			\subfloat[Block Diagram]{
				\resizebox{0.32\linewidth}{!}{
					\input{assets/illustration/block_diagram.tex}
				}
				\label{fg:block_diagram}
			}
			\subfloat[Equivalent Circuit]{
				\resizebox{0.37\linewidth}{!}{
					\input{assets/illustration/equivalent_circuit.tex}
				}
				\label{fg:equivalent_circuit}
			}
			\subfloat[Scatter Model]{
				\resizebox{0.28\linewidth}{!}{
					\input{assets/illustration/scatter_model.tex}
				}
				\label{fg:scatter_model}
			}
			\caption{
			Block diagram, equivalent circuit, and scatter model of a RIScatter node.
			The solid and dashed vectors represent signal and energy flows.
			The scatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\text{I}}$ and magnetic field $\vec{H}_{\text{I}}$ \cite{Huang2021}.
			}
			\label{fg:riscatter_node}
		\end{figure*}
		Fig.~\ref{fg:scatter_comparison} compares the reflection state distribution and reflection pattern of RIScatter and other applications.
		\begin{figure}[!t]
			\centering
			\subfloat[Reflection State Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
				\label{fg:input_distribution}
			}
			\\
			\subfloat[Reflection Pattern]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_structure.tex}
				}
				\label{fg:time_structure}
			}
			\caption{
				Reflection state distribution and reflection pattern over time of scattering applications.
				``PB'', ``BB'', and ``CB'' refer to primary block, backscatter block, and channel block, respectively.
				\gls{bc} employs all possible states as information codewords, \gls{ris} treats them as beamformer codewords, and RIScatter simultaneously exploits both benefits.
			}
			\label{fg:scatter_comparison}
		\end{figure}
		Instead of using fully random or fully deterministic reflection pattern over time, each RIScatter node \emph{semi-randomly} chooses the reflection state for each backscatter block with \emph{guidance of input probability} $P(\Gamma_m)$ at state $m$.
		Such an adaptive backscatter channel coding includes the degenerate distribution of \gls{ris} and the uniform distribution of line-coded \gls{bc} as special cases.
		Importantly, RIScatter system design only requires the \emph{direct} transmitter-receiver and \emph{cascaded} transmitter-scatter-receiver \gls{csi}.
		For dispersed RIScatter nodes, relevant \gls{csi} can be estimated by sequential \cite{Bharadia2015,Yang2015b,Guo2019g} or parallel approaches \cite{Jin2021a} originally proposed for \gls{bc}.
		For co-located RIScatter nodes, the estimation can be simplified by group-based \cite{Zheng2019} and hierarchical \cite{You2019} trainings originally proposed for \gls{ris}.
